Modified replication

### 2020-11-09 rep_nosmooth/README.Rmd
update numbering
recreate-tables has to be run before figure scripts

The file numbering indicates the order in which files should be run, and correspond to the steps above. Files with the same number can be run in any order, as long as lower number files have already been run.

@@

Process results; figures, tables, etc.:

- `3-...`: the various scripts starting with "3-" recreate the various tables and figures that end up in the paper. These are written to the `rep_nosmooth/output` folder here; the `paper/` folder includes a `update-inputs.R` script that will copy needed pieces over to that folder.

@@

>>>>

The file numbering indicates the order in which files should be run, and roughly correspond to the steps above. Files with the same number can be run in any order, as long as lower number files have already been run.

@@

Recreate AUC-ROC tables:

- `3-recreate-tables.R` produces various tables summarizing the performance of the core event data models (B&S Table 1) and the structural models (B&S Table 2); some of these are used as inputs to generate figures below.

Generate figures:

- `4-...`: the various scripts starting with "4-" recreate the various figures that end up in the paper.

The processed results created in the above two sets of scripts ("3-..." and "4-...") are written to the `rep_nosmooth/output` folder here. The `paper/` folder includes a `update-inputs.R` script that will copy needed pieces over to that folder.

@@

## Variation due to random number generator seed

We consciously chose not do set a random number generator (RNG) seed in the model estimation script (`2-model-runner.R`), because the substantive results should not change as a result of the small amount of variation related to RNG state. The [variance.md](variance.md) note explores this to some extent and leads us to believe that this is the case, with variation for the Table 1 models generally less than 0.01 AUC-ROC.

Anyways, the model runner script does include a provision for setting a RNG seed, in which case the key output files will be suffixed with the RNG seed value. Note that the results processing scripts are not setup to work this these output files, but it should be fairly obvious what lines need modifications to make them work.
